Using Optimal Time Step Selection to Boost the Accuracy of Finite Difference Schemes for Time Dependent PDEs

### 2010-05-21 papers/OTSPDE/submissions/201005-Applied_Mathematics_and_Computation/cover_letter.tex
Added Applied Mathematics and Computations submission information.

\opening{Dear Applied Numerical Mathematics Editor/Referee,}

My article titled \emph{Boosting the Accuracy of Finite Difference Schemes via
Optimal Time Step Selection and Non-Iterative Defect Correction} discusses a 
simple technique for boosting the order of accuracy of finite difference 
schemes for time dependent PDEs by choosing an optimal, \emph{fixed} time step
and adding defect correction terms in a \emph{non-iterative} manner.  As 
discussed in the paper, a careful choice of time step can dramatically 
reduce the numerical error of simple finite difference schemes and make 
it possible to achieve high-order accuracy using only formally low-order 
finite difference stencils and time integration schemes.

@@

>>>>

\opening{Dear Applied Mathematics and Computations Editor/Reviewer,}

My article titled \emph{Using Optimal Time Step Selection to Boost the
Accuracy of Finite Difference Schemes for Time Dependent PDEs} discusses a 
simple, systematic technique for boosting the order of accuracy of finite
difference schemes for time dependent PDEs by choosing an optimal, 
\emph{fixed} time step (and possibly adding defect correction terms in a 
\emph{non-iterative} manner).  As discussed in the paper, a careful choice of
time step can reduce the order of the numerical error of simple finite 
difference schemes and make it possible to achieve high-order accuracy using 
only formally low-order finite difference stencils and time integration 
schemes.

@@

In addition to being an interesting method, I believe that this method has
value in light of recent advances in GPGPU computing.  Because modern GPU
hardware is more compatible with explicit time stepping schemes, the ability
of optimal time step selection to dramaticaly boost the accuracy of simple
explicit schemes makes it a powerful tool for achieving high-performance
on GPUs.
